---
title: "Correlations and Scatterplots"
author: "Luke VandenHeuvel"
date: "10/9/2021"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
knitr::opts_chunk$set(echo = TRUE)
BodyFat <- read.csv("BodyFat3.0.csv")
```

## R Markdown

These plots are all of the plots with correlations below 0.7 from the largest down to the smallest. Any variables with correlation above 0.7 I deemed to be too highly correlated to include in the same models.

```{r}
print("Chest~Wrist Correlation:")
plot(BodyFat$Chest.Inch.,BodyFat$Wrist.Inch.)
cor(BodyFat$Chest.Inch.,BodyFat$Wrist.Inch.)
```

```{r}
print("Weight~Forearm Correlation:")
plot(BodyFat$WEIGHT,BodyFat$Forearm.Inch.)
cor(BodyFat$WEIGHT,BodyFat$Forearm.Inch.)
```

```{r}
print("Hip~Wrist Correlation:")
plot(BodyFat$Hip.Inch.,BodyFat$Wrist.Inch.)
cor(BodyFat$Hip.Inch.,BodyFat$Wrist.Inch.)
```

```{r}
print("Adiposity~Wrist Correlation:")
plot(BodyFat$ADIPOSITY,BodyFat$Wrist.Inch.)
cor(BodyFat$ADIPOSITY,BodyFat$Wrist.Inch.)
```

```{r}
print("Abdomen~Wrist Correlation:")
plot(BodyFat$Abdomen.Inch.,BodyFat$Wrist.Inch.)
cor(BodyFat$Abdomen.Inch.,BodyFat$Wrist.Inch.)
```

```{r}
print("Weight~Ankle Correlation:")
plot(BodyFat$WEIGHT,BodyFat$Ankle.Inch.)
cor(BodyFat$WEIGHT,BodyFat$Ankle.Inch.)
```

```{r}
print("Forearm~Wrist Correlation:")
plot(BodyFat$Forearm.Inch.,BodyFat$Wrist.Inch.)
cor(BodyFat$Forearm.Inch.,BodyFat$Wrist.Inch.)
```

```{r}
print("Chest~Forearm Correlation:")
plot(BodyFat$Chest.Inch.,BodyFat$Forearm.Inch.)
cor(BodyFat$Chest.Inch.,BodyFat$Forearm.Inch.)
```

```{r}
print("Ankle~Wrist Correlation:")
plot(BodyFat$Ankle.Inch.,BodyFat$Wrist.Inch.)
cor(BodyFat$Ankle.Inch.,BodyFat$Wrist.Inch.)
```

```{r}
print("Adiposity~Forearm Correlation:")
plot(BodyFat$ADIPOSITY,BodyFat$Forearm.Inch.)
cor(BodyFat$ADIPOSITY,BodyFat$Forearm.Inch.)
```

```{r}
print("Hip~Ankle Correlation:")
plot(BodyFat$Hip.Inch.,BodyFat$Ankle.Inch.)
cor(BodyFat$Hip.Inch.,BodyFat$Ankle.Inch.)
```

```{r}
print("Hip~Forearm Correlation:")
plot(BodyFat$Hip.Inch.,BodyFat$Forearm.Inch.)
cor(BodyFat$Hip.Inch.,BodyFat$Forearm.Inch.)
```

```{r}
print("Abdomen~Forearm Correlation:")
plot(BodyFat$Abdomen.Inch.,BodyFat$Forearm.Inch.)
cor(BodyFat$Abdomen.Inch.,BodyFat$Forearm.Inch.)
```

```{r}
print("Adiposity~Ankle Correlation:")
plot(BodyFat$ADIPOSITY,BodyFat$Ankle.Inch.)
cor(BodyFat$ADIPOSITY,BodyFat$Ankle.Inch.)
```

```{r}
print("Chest~Ankle Correlation:")
plot(BodyFat$Chest.Inch.,BodyFat$Ankle.Inch.)
cor(BodyFat$Chest.Inch.,BodyFat$Ankle.Inch.)
```

```{r}
print("Abdomen~Ankle Correlation:")
plot(BodyFat$Abdomen.Inch.,BodyFat$Ankle.Inch.)
cor(BodyFat$Abdomen.Inch.,BodyFat$Ankle.Inch.)
```

```{r}
print("Ankle~Forearm Correlation:")
plot(BodyFat$Ankle.Inch.,BodyFat$Forearm.Inch.)
cor(BodyFat$Ankle.Inch.,BodyFat$Forearm.Inch.)
```

```{r}
print("Height~Wrist Correlation:")
plot(BodyFat$HEIGHT,BodyFat$Wrist.Inch.)
cor(BodyFat$HEIGHT,BodyFat$Wrist.Inch.)
```

```{r}
print("Weight~Height Correlation:")
plot(BodyFat$WEIGHT,BodyFat$HEIGHT)
cor(BodyFat$WEIGHT,BodyFat$HEIGHT)
```

All other variables with a lower correlation are compared to the height variable. Assuming that height alone will not be one of the variables in our model (due to the poor correlation between height and bodyfat) I will not plot the remaining scatterplots.


